### 2024-10-28 main_widom_morse.tex
work on introduction

% directly from the equation of state 
[Here will be a small paragraph about challenges on developing the global equation of state directly predicting crossover line in supercritical fluids]
% we would like to share an idea

[Here a short paragraph that this work is a logical consequence of our previous works on the equation of state and response functions for the cell fluid model with interaction expressed by the modified Morse potential]

In Section~\ref{sec:eos}, we present the modified Morse potential used in our work, the explicit expression for the equation of state, and plot of pressure isotherms at temperatures below and above the critical one. In Section~\ref{sec:widom}, we display the Widom line as the maxima locus of the isothermal compressibility and introduce the supercritical crossover line obtained directly from the equation of state of the cell fluid model.

@@

In the present work we take advantage of the results obtained in \cite{KD20,DKRP24arxiv,DKRP24}. In \cite{KD20}, the phase space of collective variables%\footnote{The term "collective variables" is commonly used to refer to a specific category of variables unique to each physical system. In the context of liquid-vapour systems, these collective variables are linked to modes of density deviation from the critical density. This set of collective variables encompasses those which average values are connected to order parameters.Thus, the depiction of the phase transition within the phase space of collective variables appears compelling.} 
is used for calculating the grand partition function of a cell fluid model in the zero-mode approximation and consequently deriving the explicit forms of the equation of state (EoS) both in pressure-temperature-chemical potential terms and pressure-temperature-density terms. The resulting EoSs are applicable in a wide range of temperatures below and above the critical point. In \cite{DKRP24arxiv,DKRP24}, we used these equations as the basis for the calculation and graphical representation of the thermodynamic response functions (isothermal compressibility, thermal pressure coefficient, thermal expansion) of the cell fluid model with modified Morse potential in the supercritical region.

@@

%\bibliographystyle{elsarticle-num}
\bibliographystyle{plain}
\bibliography{extracted}

>>>>

In our previous work~\cite{KD20}, the equation of state for a many-particle system interacting via a modified Morse potential was developed in the framework of a cell model. Recently~\cite{DKRP24,DKRP24arxiv}, the thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, have been calculated for the same model system. The isothermal compressibility and thermal expansion coefficient both develop a maximum in some region beyond critical point. On the one hand, such response function maxima, as mentioned above, are considered as good candidates for crossover lines between gas-like and liquid-like behaviors in the supercritical region. On the other hand, they are also considered as natural continuation of the coexistence line. Since our model allows for analytical expressions for many thermodynamic quantities~\cite{KD20,DKRP24}, it is straightforward to calculate and build such continuations. As a logical sequence of our previous works for the cell model with the modified Morse potential, in this paper we present results for two lines that can be cosidered as continuations of the coexistence line beyond the critical point in the pressure-temperature plane. The first one is the locus of the isothermal compressibility maxima. This line, as will be shown, ends (disappears, ceases to exist) at some temperature above the critical one. The second one is a line that is derived from the same condition that the first-order phase transition line below the critical point - the condition on the effective chemical potential $M=0$. This line can be extended into the supercritical region without any limits in temperature or pressure.

In Section~\ref{sec:eos}, we recall the form of the modified Morse potential, present the explicit expression for the equation of state, and illustrate pressure isotherms at temperatures below and above the critical one. In Section~\ref{sec:widom}, we display the Widom line as the maxima locus of the isothermal compressibility and introduce the supercritical crossover line obtained directly from the equation of state of the cell fluid model applying the proper condition on the effective chemical potential.

@@

In the present work we take advantage of the results obtained in \cite{KD20,DKRP24arxiv,DKRP24}. In \cite{KD20}, the phase space of collective variables%\footnote{The term "collective variables" is commonly used to refer to a specific category of variables unique to each physical system. In the context of liquid-vapour systems, these collective variables are linked to modes of density deviation from the critical density. This set of collective variables encompasses those which average values are connected to order parameters.Thus, the depiction of the phase transition within the phase space of collective variables appears compelling.} 
is used for calculating the grand partition function of a cell fluid model in the zero-mode approximation and consequently deriving the explicit forms of the equation of state (EoS) both in pressure-temperature-chemical potential terms and pressure-temperature-density terms. The resulting EoSs are applicable in a wide range of temperatures below and above the critical point. In~\cite{DKRP24arxiv,DKRP24}, we used these equations as the basis for the calculation and graphical representation of the thermodynamic response functions (isothermal compressibility, thermal pressure coefficient, thermal expansion) of the cell fluid model with modified Morse potential in the supercritical region.

@@

%\bibliographystyle{elsarticle-num}
%\bibliographystyle{plain}
\bibliographystyle{gost2008}
\bibliography{extracted}
